### 2018-04-17 paper/paper.tex
1.1 question 2 answered
equeation env -> \[\]

\section{Linear Regression}
\subsection{Derivation of Regularized Linear Regression}
\begin{itemize}
  \item Preliminary questions
    \begin{itemize}
      \item for each i, \(\bm{X}^{(i)}\) is n+1 dimensional column vector. For
        notaion convenience, all \(\bm{X}_0^{(i)}\) is set to \(0\).
      \item The gradient of \(J(\bm{\theta})\) is \[
          \frac{\partial J(\bm{\theta})}{\partial \bm{\theta}} = \langle
          \frac{\partial J(\bm{\theta})}{\partial \theta_0}, \quad
          \frac{\partial J(\bm{\theta})}{\partial \theta_1}, \quad
          \cdots, \quad
          \frac{\partial J(\bm{\theta})}{\partial \theta_n}
          \rangle
        \]. It is n+1 dimensional column vector.
      \item In gradient, function \(f\) is
        \(\mathbb{R}^n\rightarrow\mathbb{R} \) and the gradient itself is vector.
        The jacobian matrix of function
        \(\bm{f}\colon\mathbb{R}^n\rightarrow\mathbb{R}^m\) is
        \[[
          \quad \frac{\partial \bm{f}}{\partial x_1} \quad
          \frac{\partial \bm{f}}{\partial x_2} \quad
          \cdots \quad \frac{\partial \bm{f}}{\partial x_n} \quad
          ] =
          \begin{bmatrix}
            \frac{\partial f_1}{\partial x_1} & \cdots & \frac{\partial f_1}{\partial x_n} \\
            \vdots & \ddots & \vdots \\
            \frac{\partial f_m}{\partial x_1} & \cdots & \frac{\partial f_m}{\partial x_n}
          \end{bmatrix}
          \]
          where \(\bm{f} = <f_1, f_2, \cdots, f_m>\) and \(\bm{x} = <x_1, x_2, \cdots, x_n>\).
          When \(m=0\), Jacobian matrix and gradient are same.
        \item \(\bm{X\theta}\) is \(m\) dimension vector. The dimension of jacobian
          matrix \(\frac{\partial \bm{X\theta}}{\partial \bm{\theta}}\) is \(n+1 \times m\).
          In this case, \(\frac{\partial \bm{X\theta}}{\partial \bm{\theta}}\) is same with \(\bm{X}\).
    \end{itemize}
  \item 2
  \item 3
\end{itemize}

@@

\section{Logistic Regression}
\subsection{Derivation of Gradient}
\begin{equation}
  \begin{split}
    J(\bm{\theta}) &= -\frac{1}{m} \sum_{i=1}^{m} \left( y^{(i)} \log (h_{\bm{\theta}}(\bm{x}^{(i)}))
    + (1-y^{(i)} ) \log (1 - h_{\bm{\theta}}(\bm{x}^{(i)}))  \right) \\
    &=  -\frac{1}{m} \sum_{i=1}^{m} \left( y^{(i)} \log (\sigma(\bm{x}^{(i)T}\bm{\theta}))
    + (1-y^{(i)} ) \log (1 - \sigma(\bm{x}^{(i)T}\bm{\theta})  \right)
  \end{split}
\end{equation}
The partial derivative of the cost function with respect $\theta_j$ is
\begin{equation}
  \begin{split}
    \frac{\partial J(\bm{\theta})}{\partial \theta_j }
    &= -\frac{1}{m} \sum_{i=1}^m \left(
    y^{(i)} \frac{1}{\sigma(\bm{x}^{(i)T}\bm{\theta})} \frac{\partial \sigma(\bm{x}^{(i)T}\bm{\theta})}{\partial \theta_j}
    - (1-y^{(i)}) \frac{1}{1-\sigma(\bm{x}^{(i)T}\bm{\theta})} \frac{\partial \sigma(\bm{x}^{(i)T}\bm{\theta})}{\partial \theta_j}
    \right) \\
    &= -\frac{1}{m} \sum_{i=1}^m \left(
    y^{(i)} \frac{\sigma(\bm{x}^{(i)T}\bm{\theta}) \cdot (1 - \sigma(\bm{x}^{(i)T}\bm{\theta}))}{\sigma(\bm{x}^{(i)T}\bm{\theta})} \cdot \frac{\partial \bm{x}^{(i)T}\bm{\theta}}{\partial \theta_j}
    - (1 - y^{(i)}) \frac{\sigma(\bm{x}^{(i)T}\bm{\theta}) \cdot (1 - \sigma(\bm{x}^{(i)T}\bm{\theta}))}{1 - \sigma(\bm{x}^{(i)T}\bm{\theta})} \cdot \frac{\bm{x}^{(i)T}\bm{\theta}}{\partial \theta_j}
    \right) \\
    &= -\frac{1}{m} \sum_{i=1}^{m} \left(
    y^{(i)} \frac{\sigma(\bm{x}^{(i)T}\bm{\theta}) \cdot (1 - \sigma(\bm{x}^{(i)T}\bm{\theta})) \cdot x_j^{(i)}}{\sigma(\bm{x}^{(i)T}\bm{\theta})}
    - (1 - y^{(i)}) \frac{\sigma(\bm{x}^{(i)T}\bm{\theta}) \cdot (1 - \sigma(\bm{x}^{(i)T}\bm{\theta})) \cdot x_j^{(i)}}{1 - \sigma(\bm{x}^{(i)T}\bm{\theta})}
    \right) \\
    &= - \frac{1}{m} \sum_{i=1}^m \left(
    y^{(i)} - y^{(i)} \sigma(\bm{x}^{(i)T}\bm{\theta}) + y^{(i)} \sigma(\bm{x}^{(i)T}\bm{\theta}) - \sigma(\bm{x}^{(i)T}\bm{\theta}) \right)\cdot x_j^{(i)} \\
    &= -\frac{1}{m} \sum_{i=1}^m \left(
    y^{(i)} - \sigma(\bm{x}^{(i)T}\bm{\theta})\right) \cdot x_j^{(i)} \\
    &= \frac{1}{m} \sum_{i=1}^m \left( h_{\bm{\theta}}(\bm{x}^{(i)}) - y^{(i)}\right) \cdot x_j^{(i)}
  \end{split}
\end{equation}
Thus, the gradient of the cost function is
\begin{equation}
  \frac{\partial J(\bm{\theta})}{\partial \theta_j } = \frac{1}{m} \sum_{i=1}^m \left( h_{\bm{\theta}}(\bm{x}^{(i)}) - y^{(i)}\right) \cdot x_j^{(i)}
\end{equation}
\subsection{Logistic Regression training with gradient descent and scipy.optimize}
\subsubsection{Gradient descent}
\paragraph
1The function check\_gradient in toolbox.py is here to test if your gradient is well computed. Explain what it is doing
\paragraph
2The following plots demonstrate the results of Logistic Regression with degree 1 and learning rate $\eta$ = 1 for 20 and 2000 iterations :

>>>>

\section{Linear Regression}
\subsection{Derivation of Regularized Linear Regression}
\begin{itemize}
  \item Preliminary questions
    \begin{itemize}
      \item for each i, \(\bm{X}^{(i)}\) is n+1 dimensional column vector. For
        notaion convenience, all \(\bm{X}_0^{(i)}\) is set to \(0\).
      \item The gradient of \(J(\bm{\theta})\) is \[
          \frac{\partial J(\bm{\theta})}{\partial \bm{\theta}} = \langle
          \frac{\partial J(\bm{\theta})}{\partial \theta_0}, \quad
          \frac{\partial J(\bm{\theta})}{\partial \theta_1}, \quad
          \cdots, \quad
          \frac{\partial J(\bm{\theta})}{\partial \theta_n}
          \rangle
        \]. It is n+1 dimensional column vector.
      \item In gradient, function \(f\) is
        \(\mathbb{R}^n\rightarrow\mathbb{R} \) and the gradient itself is vector.
        The jacobian matrix of function
        \(\bm{f}\colon\mathbb{R}^n\rightarrow\mathbb{R}^m\) is
        \[[
          \quad \frac{\partial \bm{f}}{\partial x_1} \quad
          \frac{\partial \bm{f}}{\partial x_2} \quad
          \cdots \quad \frac{\partial \bm{f}}{\partial x_n} \quad
          ] =
          \begin{bmatrix}
            \frac{\partial f_1}{\partial x_1} & \cdots & \frac{\partial f_1}{\partial x_n} \\
            \vdots & \ddots & \vdots \\
            \frac{\partial f_m}{\partial x_1} & \cdots & \frac{\partial f_m}{\partial x_n}
          \end{bmatrix}
          \]
          where \(\bm{f} = <f_1, f_2, \cdots, f_m>\) and \(\bm{x} = <x_1, x_2, \cdots, x_n>\).
          When \(m=0\), Jacobian matrix and gradient are same.
        \item \(\bm{X\theta}\) is \(m\) dimension vector. The dimension of jacobian
          matrix \(\frac{\partial \bm{X\theta}}{\partial \bm{\theta}}\) is \(n+1 \times m\).
          In this case, \(\frac{\partial \bm{X\theta}}{\partial \bm{\theta}}\) is same with \(\bm{X}\).
    \end{itemize}
  \item When the gradient of the cost function is zero, the cost function is minimized.
    \begin{align*}
      \frac{\partial \bm{X\theta}}{\partial \bm{\theta}} = 0 \\
      \frac{2}{m}(\bm{X\theta}-\bm{y})^T \cdot \bm{X} + \frac{2\lambda}{m}\bm{\theta} = 0 \\
      \frac{2}{m}(\bm{X}^T\bm{X\theta} - \bm{X}^T\bm{y}) + \frac{2\lambda}{m}\bm{\theta} = 0 \\
      \bm{X}^T\bm{X\theta} - \bm{X}^T\bm{y} + \lambda\bm{\theta} = 0 \\
      \bm{X}^T\bm{X\theta} - \bm{X}^T\bm{y} + \lambda\bm{I\theta} = 0 \\
      (\bm{X}^T\bm{X} + \lambda\bm{I})\bm{\theta} = \bm{X}^T\bm{y} \\
      \bm{\theta} = (\bm{X}^T\bm{X} + \lambda\bm{I})^{-1}\bm{X}^T\bm{y}
    \end{align*}
    As long as \(\bm{X}^T\bm{X} + \lambda\bm{I}\) is invertable, the optimal parameters
    \(\bm{\theta}^* = (\bm{X}^T\bm{X} + \lambda\bm{I})^{-1}\bm{X}^T\bm{y}\)
  \item 3
\end{itemize}

@@

\section{Logistic Regression}
\subsection{Derivation of Gradient}
\[
  \begin{split}
    J(\bm{\theta}) &= -\frac{1}{m} \sum_{i=1}^{m} \left( y^{(i)} \log (h_{\bm{\theta}}(\bm{x}^{(i)}))
    + (1-y^{(i)} ) \log (1 - h_{\bm{\theta}}(\bm{x}^{(i)}))  \right) \\
    &=  -\frac{1}{m} \sum_{i=1}^{m} \left( y^{(i)} \log (\sigma(\bm{x}^{(i)T}\bm{\theta}))
    + (1-y^{(i)} ) \log (1 - \sigma(\bm{x}^{(i)T}\bm{\theta})  \right)
  \end{split}
\]
The partial derivative of the cost function with respect $\theta_j$ is
\[
  \begin{split}
    \frac{\partial J(\bm{\theta})}{\partial \theta_j }
    &= -\frac{1}{m} \sum_{i=1}^m \left(
    y^{(i)} \frac{1}{\sigma(\bm{x}^{(i)T}\bm{\theta})} \frac{\partial \sigma(\bm{x}^{(i)T}\bm{\theta})}{\partial \theta_j}
    - (1-y^{(i)}) \frac{1}{1-\sigma(\bm{x}^{(i)T}\bm{\theta})} \frac{\partial \sigma(\bm{x}^{(i)T}\bm{\theta})}{\partial \theta_j}
    \right) \\
    &= -\frac{1}{m} \sum_{i=1}^m \left(
    y^{(i)} \frac{\sigma(\bm{x}^{(i)T}\bm{\theta}) \cdot (1 - \sigma(\bm{x}^{(i)T}\bm{\theta}))}{\sigma(\bm{x}^{(i)T}\bm{\theta})} \cdot \frac{\partial \bm{x}^{(i)T}\bm{\theta}}{\partial \theta_j}
    - (1 - y^{(i)}) \frac{\sigma(\bm{x}^{(i)T}\bm{\theta}) \cdot (1 - \sigma(\bm{x}^{(i)T}\bm{\theta}))}{1 - \sigma(\bm{x}^{(i)T}\bm{\theta})} \cdot \frac{\bm{x}^{(i)T}\bm{\theta}}{\partial \theta_j}
    \right) \\
    &= -\frac{1}{m} \sum_{i=1}^{m} \left(
    y^{(i)} \frac{\sigma(\bm{x}^{(i)T}\bm{\theta}) \cdot (1 - \sigma(\bm{x}^{(i)T}\bm{\theta})) \cdot x_j^{(i)}}{\sigma(\bm{x}^{(i)T}\bm{\theta})}
    - (1 - y^{(i)}) \frac{\sigma(\bm{x}^{(i)T}\bm{\theta}) \cdot (1 - \sigma(\bm{x}^{(i)T}\bm{\theta})) \cdot x_j^{(i)}}{1 - \sigma(\bm{x}^{(i)T}\bm{\theta})}
    \right) \\
    &= - \frac{1}{m} \sum_{i=1}^m \left(
    y^{(i)} - y^{(i)} \sigma(\bm{x}^{(i)T}\bm{\theta}) + y^{(i)} \sigma(\bm{x}^{(i)T}\bm{\theta}) - \sigma(\bm{x}^{(i)T}\bm{\theta}) \right)\cdot x_j^{(i)} \\
    &= -\frac{1}{m} \sum_{i=1}^m \left(
    y^{(i)} - \sigma(\bm{x}^{(i)T}\bm{\theta})\right) \cdot x_j^{(i)} \\
    &= \frac{1}{m} \sum_{i=1}^m \left( h_{\bm{\theta}}(\bm{x}^{(i)}) - y^{(i)}\right) \cdot x_j^{(i)}
  \end{split}
\]
Thus, the gradient of the cost function is \[
  \frac{\partial J(\bm{\theta})}{\partial \theta_j } = \frac{1}{m} \sum_{i=1}^m \left( h_{\bm{\theta}}(\bm{x}^{(i)}) - y^{(i)}\right) \cdot x_j^{(i)}
\]

\subsection{Logistic Regression training with gradient descent and scipy.optimize}
\subsubsection{Gradient descent}
\paragraph
1The function check\_gradient in toolbox.py is here to test if your gradient is well computed. Explain what it is doing
\paragraph
2The following plots demonstrate the results of Logistic Regression with degree 1 and learning rate $\eta$ = 1 for 20 and 2000 iterations :
